Thesis outline

### 2017-06-12 KellyDouglass/Thesis/Thesis_sections/Introduction.tex
Added intro figures
Updated Intro, Conclusion

\begin{figure}
%    \includegraphics[width=0.9\textwidth]{Images/Intro/Millenium_simulation}
    \caption[Dark matter simulation]{Snapshots of a portion of the Millenium 
    Simulation showing the dark matter distribution at different points in time 
    from 0.21 Gyr after the Big Bang to the present.  Small perturbations in the 
    initial distribution of dark matter are amplified as the universe expands.  
    Gravity causes the slightly overdense regions to contract while 
    simultaneously causing the underdense regions to expand.}
    \label{fig:DMsim}
\end{figure}

Large sky surveys \citep[such as the Sloan Digital Sky Survey --- 
SDSS][]{York00} have revealed a non-uniform distribution of galaxies throughout 
the universe.  Taking on a shape similar to that of a three-dimensional cosmic 
web \citep{Bond96} or a sponge, galaxies clump together in clusters and along 
filaments, leaving void regions between them.  Evidence of this distribution can 
be seen in Fig. \ref{fig:SDSS_map} for galaxies in the SDSS Data Release 7 
\citep[SDSS DR7][]{Abazajian09}.  Based on these observations, dark matter 
simulations have been constructed which successfully reproduce the same 
large-scale structure.  If we start with a mostly uniform distribution of dark 
matter at the Big Bang, Fig. \ref{fig:DMsim} outlines the evolution of that dark 
matter up to present day.  These snapshots from the Millenium Simulation project 
\citep{Springel05} show that small perturbations in the initial distribution of 
dark matter are amplified as the universe expands.  Gravity causes the slightly 
overdense regions to collapse while simultaneously causing the underdense 
regions to expand.  Due to dark matter's strong gravitational interaction, we 
believe that the baryonic mattter (that which interacts electromagnetically) 
will trace the dark matter distribution, resulting in the galaxy distribution we 
observe today.

% Void galaxies
\begin{figure}
%    \includegraphics[width=0.9\textwidth]{Images/Intro/void_slice}
    \caption[Sky map highlighting voids and void galaxies]{A 10 \hMpc slice of 
    SDSS DR7 \citep[Fig. 1]{Moorman14} with void regions highlighted in blue 
    circles.  Void galaxies are shown as red points while wall galaxies are 
    black.  Existing in the cosmological voids (space between the galactic 
    filaments), void galaxies are though to demonstrate the fundamental 
    characteristics of galactic evolution.}
\end{figure}

The galaxies within the underdense void environments are named ``void 
galaxies.''  Existing in the cosmological voids, void galaxies are thought to 
demonstrate the fundamental characteristics of galactic evolution.  Cosmic voids 
are an important environment for studying galaxy formation \citep[see][for a 
review]{vandeWeygaert11}.  Gravitational clustering proceeds as if in a very low 
density universe, where the amassment of gravitationally bound dark matter halos 
ends relatively early and there is little subsequent interaction between the 
galaxies due to the lower density and the faster local Hubble expansion.  
Therefore, $\Lambda$CDM cosmology predicts that galaxies formed in voids should 
have lower mass and be retarded in their star formation when compared to those 
in denser regions \cite[e.g.,][]{Gottlober03,Goldberg05,Cen11}.  
\cite{Goldberg04} show that a void region that is only 10\% of the mean density 
of the universe with $\Omega_{matter} = 0.3$, $h = 0.7$ dynamically evolves as 
if $\Omega_{matter} = 0.02$, $\Omega_\Lambda = 0.48$, and $h = 0.84$.  
Additionally, hydrodynamical cosmological simulations by \cite{Cen11} show that 
the gas in voids remains below the critical entropy threshold, allowing void 
galaxies to continue to form stars.  Void galaxies evolve in a relatively 
pristine environment where interactions are rare and star formation proceeds up 
to the present epoch because void galaxies are able to retain their gas.  This 
contrasts the denser environments, where the chemical composition and evolution 
of galaxies are drastically altered due to mergers and tidal stripping and/or 
ram-pressure stripping.

@@

% Dwarf galaxies
\begin{figure}
    \includegraphics[width=0.65\textwidth]{Images/Intro/1sig_13-23_SDSS_Mr_hist_count_fill}
    \caption[Absolute magnitude distribution of galaxies in SDSS DR7]{Absolute 
    magnitude ($M_r$) distribution of galaxies in SDSS DR7, separated into void 
    and wall environments.  Dwarf galaxies are defined as galaxies with absolute 
    magnitudes fainter than -17 ($M_r > -17$).  For reference, the Milky Way has 
    an absolute magnitude $M_r \approx -20$.}
\end{figure}

In particular, we are going to study the effects of the large-scale environment 
on the formation and evolution of dwarf galaxies.  Defined to be galaxies with 
absolute magnitudes fainter than -17 ($M_r > -17$), the lower stellar masses of 
these systems correspond to more shallow gravitational potential wells.  This 
causes any environmental effects to have a more significant influence on dwarf 
galaxies than on galaxies with larger stellar masses.  In addition, studying 
void dwarf galaxies will complement previous studies of dwarfs in groups and 
clusters because the assembly histories of low-mass galaxies are predicted to 
be very different \citep[e.g.,][]{Gao07,Lackner12}.  Observations to date also 
show that the properties of dwarf galaxies vary dramatically with the 
environment \citep[e.g.,][]{Ann08,Geha12}.

@@

The first stars that formed are thought to have been composed of only hydrogen 
(and maybe some trace amount of helium).  As stars burn, nucleosythesis creates 
heavier elements at the core.  When the stars die and expel some or all of their 
contents, the heavier elements are distributed between the surrounding 
interstellar gas and the surrounding circumgalactic medium.  When new stars form 
from this gas, they include both hydrogen and some of the heavier elements.  By 
measuring the fraction of elements heavier than helium (``metals'') relative to 
the hydrogen content (the metallicity), we measure the integrated star formation 
history of the galaxy.

\begin{figure}
    \includegraphics[width=0.9\textwidth]{Images/Intro/Kirchoff}
    \caption[Kirchoff's laws of spectroscopy]{Three different viewpoints of the 
    light emitted from a star and/or a cool cloud of gas, representing 
    Kirchoff's laws of spectroscopy.  A star emits light across all wavelengths, 
    so the resulting spectrum is known as a continuous spectrum.  Star's light 
    that has passed through a cloud of cool gas before being observed is an 
    absorption spectrum, where the elements in the cloud have absorbed some of 
    the light at specific wavelengths (corresponding to the particular elements 
    present in the gas).  If observed off the line-of-sight of the star, the 
    light emitted from the cloud of cooler gas is named an emission spectrum, 
    where the gas is re-radiating the light it absorbed from the star.}
    \label{fig:Kirchoff}
\end{figure}

@@

\begin{figure}
%    \includegraphics[width=0.9\textwidth]{Images/Intro/spectrum}
    \caption[Sample (void) dwarf galaxy spectrum]{Example SDSS DR7 spectrum --- 
    this is a void dwarf galaxy whose gas-phase chemical abundances are slightly 
    above average.  The [\ion{O}{3}] $\lambda$4363 auroral line is circled in 
    red, while the [\ion{O}{3}] $\lambda \lambda$4959,5007 doublet is circled in 
    yellow.}
    \label{fig:spectrum}
\end{figure}

The ion transitions observed in the optical part of the spectrum (which is where 
SDSS DR7 operates) consist of forbidden transitions.  As explained in detail in 
Section \ref{sec:physics}, forbidden transitions have much longer lifetimes than 
the allowed electron transitions.  These transitions depend strongly on the 
temperature and density of the electron gas, because the long lifetimes allow 
the atoms to easily collisionally de-excite.  By taking the ratio of the 
[\ion{O}{3}] $\lambda$4363 auroral line to the [\ion{O}{3}] 
$\lambda \lambda$4959,5007 doublet, we can get an estimate of the temperature of 
the gas.  These lines are highlighted on the example SDSS DR7 spectrum shown in 
Fig. \ref{fig:spectrum}.

@@

% Outline of Thesis
% Pose the problem - how does the large-scale environment affect galaxy evolution?
We want to understand how dark matter affects the evolution of a galaxy, and 
what influence it has on a galaxy's star formation.  To do this, we compare the 
properties of galaxies living in voids with galaxies in denser regions in an 
effort to understand how the properties of the gas and the history of star 
formation in a galaxy depend on the environment.  We then try to infer what 
these results tell us about the dark matter structure and history of the galaxy.  
In Chapter \ref{ch:Paper1}, we calculate and compare the metallicity of 135 
star-forming dwarf galaxies as a function of their large-scale environment.  We 
continue studying this galaxy sample in Chapter \ref{ch:Paper2} by estimating 
their ratios of nitrogen to oxygen and looking at how that depends on the 
large-scale environment.  To expand our dwarf galaxy sample, we derive an 
approximation for the amount of singly-ionized oxygen and repeat our analysis of 
the large-scale environmental influence on the gas-phase chemical abundances of 
1920 star-forming dwarf galaxies in Chapter \ref{ch:Paper3}.  In Chapter 
\ref{ch:smallScaleEnvironment}, we investigate how the dwarf galaxies' 
properties depend on the galaxies' distances to the nearest neighbors and 
groups.  Finally, in an effort to better understand how galaxies evolve from 
blue, star-forming systems to ``red and dead,'' we discover a way to classify 
galaxies into their location on the color-magnitude diagram in Chapter 
\ref{ch:GV}.

>>>>

\begin{figure}
    \includegraphics[width=0.9\textwidth]{Images/Intro/Millenium_simulation}
    \caption[Dark matter simulation]{Snapshots of a portion of the Millenium 
    Simulation showing the dark matter distribution at different points in time 
    from 0.21 Gyr after the Big Bang to the present.  Small perturbations in the 
    initial distribution of dark matter are amplified as the universe expands.  
    Gravity causes the slightly overdense regions to contract while 
    simultaneously causing the underdense regions to expand.}
    \label{fig:DMsim}
\end{figure}

Large sky surveys \citep[such as the Sloan Digital Sky Survey --- 
SDSS;][]{York00} have revealed a non-uniform distribution of galaxies throughout 
the universe.  Taking on a shape similar to that of a sponge or a 
three-dimensional cosmic web \citep{Bond96}, galaxies clump together in clusters 
and along filaments, leaving void regions between these large-scale structures.  
Evidence of this distribution can be seen in Fig. \ref{fig:SDSS_map} for 
galaxies in the SDSS Data Release 7 \citep[SDSS DR7;][]{Abazajian09}.  Based on 
these observations, dark matter simulations have been constructed which 
successfully reproduce the same large-scale structure.  If we start with a 
mostly uniform distribution of dark matter at the Big Bang, Fig. \ref{fig:DMsim} 
outlines the evolution of that dark matter up through the present.  These 
snapshots from the Millenium Simulation project \citep{Springel05} show that 
small perturbations in the initial distribution of dark matter are amplified as 
the universe expands.  Gravity causes the slightly overdense regions to collapse 
while simultaneously causing the underdense regions to expand.  Due to dark 
matter's strong gravitational interaction, we believe that the baryonic mattter 
(matter which interacts electromagnetically) will trace the dark matter 
distribution, resulting in the galaxy distribution we observe today.

% Void galaxies
\begin{figure}
    \includegraphics[width=0.9\textwidth]{Images/Intro/VoidFinder}
    \caption[Sky map highlighting voids and void galaxies]{A 10 \hMpc slice of 
    SDSS DR7 \citep[Fig. 1]{Moorman14} with void regions highlighted in blue 
    circles.  Void galaxies are shown as red points while wall galaxies are 
    black.  Existing in the cosmological voids (space between the galactic 
    filaments), void galaxies are though to demonstrate the fundamental 
    characteristics of galactic evolution.}
\end{figure}

Existing in the cosmological voids, void galaxies are thought to demonstrate the 
fundamental characteristics of galactic evolution.  Cosmic voids are an 
important environment for studying galaxy formation \citep[see][for a review]
{vandeWeygaert11}.  Gravitational clustering proceeds as if in a very low 
density universe, where the amassment of gravitationally bound dark matter halos 
ends relatively early and there is little subsequent interaction between the 
galaxies due to the lower density and the faster local Hubble expansion.  
Therefore, $\Lambda$CDM cosmology predicts that galaxies formed in voids should 
have lower mass and be retarded in their star formation when compared to those 
in denser regions \cite[e.g.,][]{Gottlober03,Goldberg05,Cen11}.  
\cite{Goldberg04} show that a void region that is only 10\% of the mean density 
of the universe with $\Omega_{matter} = 0.3$, $h = 0.7$ dynamically evolves as 
if $\Omega_{matter} = 0.02$, $\Omega_\Lambda = 0.48$, and $h = 0.84$.  
Additionally, hydrodynamical cosmological simulations by \cite{Cen11} show that 
void galaxies continue to form stars because the gas in voids remains below the 
critical entropy threshold.  Void galaxies evolve in a relatively pristine 
environment where interactions are rare and star formation proceeds up to the 
present epoch because void galaxies are able to retain their gas.  This 
contrasts the denser environments, where the chemical composition and evolution 
of galaxies are drastically altered due to mergers and tidal and/or ram-pressure 
stripping.

@@

% Dwarf galaxies
\begin{figure}
    \includegraphics[width=0.65\textwidth]{Images/Intro/1sig_13-23_SDSS_Mr_hist_count_fill}
    \caption[Absolute magnitude distribution of galaxies in SDSS DR7]{Absolute 
    magnitude ($M_r$) distribution of galaxies in SDSS DR7, separated into void 
    and wall environments.  Dwarf galaxies are defined as galaxies with absolute 
    magnitudes fainter than -17 ($M_r > -17$).  For reference, the Milky Way has 
    an absolute magnitude $M_r \approx -20$.}
    \label{fig:Mr_SDSS}
\end{figure}

In particular, we study the effects of the large-scale environment on the 
formation and evolution of dwarf galaxies.  Fig. \ref{fig:Mr_SDSS} shows the 
distribution of galaxies by their absolute magnitudes detected in SDSS DR7.  
Defined to be galaxies with absolute magnitudes fainter than -17 ($M_r > -17$), 
the low stellar masses of these systems correspond to more shallow gravitational 
potential wells.  This causes any environmental effects to have a more 
significant influence on dwarf galaxies than on galaxies with larger stellar 
masses.  In addition, studying void dwarf galaxies will complement previous 
studies of dwarfs in groups and clusters because the assembly histories of 
low-mass galaxies are predicted to be very different \citep[e.g.,][]{Gao07,
Lackner12}.  Observations to date also show that the properties of dwarf 
galaxies vary dramatically with the environment \citep[e.g.,][]{Ann08,Geha12}.

@@

The first stars that formed are thought to have been composed of only hydrogen 
(and possibly some trace amount of helium).  As stars burn, nucleosythesis 
creates heavier elements at the core.  When the stars die and expel their 
content, the heavier elements are distributed between the surrounding 
interstellar gas and circumgalactic medium.  When new stars form from this gas, 
they include both hydrogen and some of the heavier elements.  By measuring the 
fraction of elements heavier than helium (``metals'') relative to the hydrogen 
content (the metallicity), we measure the integrated star formation history of 
the galaxy.

\begin{figure}
    \includegraphics[width=0.9\textwidth]{Images/Intro/Kirchoff}
    \caption[Kirchoff's laws of spectroscopy]{Three different viewpoints of the 
    light emitted from a star and/or a cool cloud of gas, representing 
    Kirchoff's laws of spectroscopy.  A star emits light across all wavelengths, 
    so the resulting spectrum is known as a continuous spectrum.  Star's light 
    that has passed through a cloud of cool gas before being observed is an 
    absorption spectrum, where the elements in the cloud have absorbed some of 
    the light at specific wavelengths (corresponding to the particular elements 
    present in the gas).  If observed off the line-of-sight of the star, the 
    light emitted from the cloud of cooler gas results in an emission spectrum, 
    where the gas is re-radiating the light it absorbed from the star.}
    \label{fig:Kirchoff}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=0.9\textwidth]{Images/Intro/spectrum}
    \caption[Sample (void) dwarf galaxy spectrum]{Example SDSS DR7 spectrum --- 
    this is a void dwarf galaxy whose gas-phase chemical abundances are slightly 
    above average.  The [\ion{O}{3}] $\lambda$4363 auroral line is circled in 
    red, while the [\ion{O}{3}] $\lambda \lambda$4959,5007 doublet is circled in 
    yellow.}
    \label{fig:spectrum}
\end{figure}

The ion transitions observed in the optical part of the spectrum (where SDSS DR7 
operates) consist of forbidden transitions.  As explained in detail in Section 
\ref{sec:physics}, forbidden transitions have much longer lifetimes than the 
allowed electron transitions.  These transitions depend strongly on the 
temperature and density of the electron gas, because the long lifetimes allow 
the atoms to easily collisionally de-excite.  By taking the ratio of the 
[\ion{O}{3}] $\lambda$4363 auroral line to the [\ion{O}{3}] 
$\lambda \lambda$4959,5007 doublet, we can get an estimate of the temperature of 
the gas.  These lines are highlighted on the example SDSS DR7 spectrum shown in 
Fig. \ref{fig:spectrum}.

@@

% Outline of Thesis
% Pose the problem - how does the large-scale environment affect galaxy evolution?
We want to understand how dark matter affects the evolution of a galaxy and what 
influence it has on a galaxy's star formation.  To do this, we compare the 
properties of galaxies living in voids with galaxies in denser regions in an 
effort to understand how the properties of the gas and the history of star 
formation in a galaxy depend on the environment.  We then try to infer what 
these results tell us about the dark matter structure and history of the galaxy.  
In Chapter \ref{ch:Paper1}, we calculate and compare the metallicity of 135 
star-forming dwarf galaxies as a function of their large-scale environment.  We 
continue studying this galaxy sample in Chapter \ref{ch:Paper2} by estimating 
their ratios of nitrogen to oxygen and looking at how that depends on the 
large-scale environment.  To expand our dwarf galaxy sample, we derive an 
approximation for the amount of singly-ionized oxygen and repeat our analysis of 
the large-scale environmental influence on the gas-phase chemical abundances of 
1920 star-forming dwarf galaxies in Chapter \ref{ch:Paper3}.  In Chapter 
\ref{ch:smallScaleEnvironment}, we investigate how the dwarf galaxies' 
properties depend on the galaxies' distances to the nearest neighbors and 
groups.  Finally, in an effort to better understand how galaxies evolve from 
blue, star-forming systems to ``red and dead,'' we discover a way to classify 
galaxies into their location on the color-magnitude diagram in Chapter 
\ref{ch:GV}.

### 2017-06-12 KellyDouglass/Thesis/preamble.tex
Updated Intro, Conclusion

% Papers 1-3
We investigate how the cosmic environment affects galaxy evolution in the 
Universe by studying gas-phase chemical abundances and other galaxy properties 
as a function of the local and cosmic density of galaxies.  Using spectroscopic 
observations from the Sloan Digital Sky Survey Data Release 7, we estimate the 
oxygen and nitrogen abundances of 993 star-forming void dwarf galaxies and 759 
star-forming dwarf galaxies in denser regions.  We use the Direct $T_e$ method 
for calculating the gas-phase chemical abundances in the dwarf galaxies because 
it is best suited for low metallicity, low mass galaxies.  A substitute for the 
[\ion{O}{2}] $\lambda$3727 doublet is developed, permitting oxygen abundance 
estimates of SDSS dwarf galaxies at all redshifts with the Direct $T_e$ method.  
We find that star-forming void dwarf galaxies have slightly higher oxygen 
abundances than star-forming dwarf galaxies in denser environments, but we find 
that void dwarf galaxies have slightly lower nitrogen abundances and lower N/O 
ratios than galaxies in denser regions.  
% Small-scale enivronment
At smaller scales, we find that only the presence of a neighboring galaxy within 
0.05 \hMpc or 0.05$r_{vir}$, or the presence of a group within 0.1 \hMpc, 
incfluences a dwarf galaxy's evolution.  Dwarf galaxies within 0.05 \hMpc or 
0.05$r_{vir}$ of another galaxy tend to be bluer, have higher sSFRs, and have 
higher oxygen and nitrogen abundances than average.  In contrast, galaxies 
within 0.1 \hMpc of the center of the closest group are redder, have lower 
oxygen abundances, and have higher N/O ratios than average.
% GV
We also investigate how a galaxy transitions through the color-magnitude 
diagram, evolving from a blue, star-forming spiral or irregular galaxy in the 
blue sequence to a red elliptical galaxy in the red cloud via the green valley.  
We discover that combining a galaxy's color, color gradient, and inverse 
concentration index defines a galaxy's location on the color-magnitude diagram.  
The results indicate that there is a higher fraction of dwarf galaxies in denser 
regions than void dwarf galaxies in the green valley.
% Conclusions
From these analyses, we surmise that void dwarf galaxies experienced delayed 
star formation as predicted by the $\Lambda$CDM cosmology and a dependence of 
the large-scale environment on cosmic downsizing.  We present evidence that void 
dwarf galaxies have a higher ratio of dark matter halo mass to stellar mass when 
compared to dwarf galaxies in denser environments.

>>>>

% Papers 1-3
We investigate how the cosmic environment affects galaxy evolution in the 
Universe by studying gas-phase chemical abundances and other galaxy properties 
as a function of the local and cosmic density of galaxies.  Using spectroscopic 
observations from the Sloan Digital Sky Survey Data Release 7, we estimate the 
oxygen and nitrogen abundances of 993 star-forming void dwarf galaxies and 759 
star-forming dwarf galaxies in denser regions.  We use the Direct $T_e$ method 
for calculating the gas-phase chemical abundances in the dwarf galaxies because 
it is best suited for low metallicity, low mass galaxies.  A substitute for the 
[\ion{O}{2}] $\lambda$3727 doublet is developed, permitting oxygen abundance 
estimates of SDSS dwarf galaxies at all redshifts with the Direct $T_e$ method.  
We find that star-forming void dwarf galaxies have slightly higher oxygen 
abundances than star-forming dwarf galaxies in denser environments, but we find 
that void dwarf galaxies have slightly lower nitrogen abundances and lower N/O 
ratios than galaxies in denser regions.  
% Small-scale enivronment
At smaller scales, we find that only the presence of a neighboring galaxy within 
0.05 \hMpc or 0.05$r_{vir}$, or the presence of a group within 0.1 \hMpc, 
influences a dwarf galaxy's evolution.  Dwarf galaxies within 0.05 \hMpc or 
0.05$r_{vir}$ of another galaxy tend to be bluer, have higher sSFRs, and have 
higher oxygen and nitrogen abundances than average.  In contrast, galaxies 
within 0.1 \hMpc of the center of the closest group are redder, have lower 
oxygen abundances, and have higher N/O ratios than average.
% GV
We also investigate how a galaxy transitions through the color-magnitude 
diagram, evolving from a blue, star-forming spiral or irregular galaxy in the 
blue sequence to a red elliptical galaxy in the red cloud through the green 
valley.  We discover that combining a galaxy's color, color gradient, and 
inverse concentration index defines a galaxy's location on the color-magnitude 
diagram.  The results indicate that there is a higher fraction of dwarf galaxies 
in denser regions than void dwarf galaxies in the green valley.
% Conclusions
From these analyses, we surmise that void dwarf galaxies experience delayed star 
formation as predicted by the $\Lambda$CDM cosmology and a dependence of the 
large-scale environment on cosmic downsizing.  We present evidence that void 
dwarf galaxies have a higher ratio of dark matter halo mass to stellar mass when 
compared to dwarf galaxies in denser environments.

### 2017-06-12 KellyDouglass/Thesis/simulations.tex
Updated Intro, Conclusion

% Hierarchical formation of halos
It is impossible to directly observe the formation of a galaxy.  Based on 
detected merging galaxies, the astronomical community has surmised the galaxies 
have increased their mass largely due to the merging of smaller galaxies.  
\cite{deRossi07} performed $\Lambda$CDM simulations of hierarchical galaxy 
formation.  They find that the growth of systems by aggregation is responsible 
for the mass-metallicity relation.  Less massive systems tend to increase their 
stellar mass by either gas-rich mergers or secular evolution, resulting in a 
stronger correlation between stellar mass and metallicity.  Evidence of this is 
seen in the mass-metallicity relation of \cite{Tremonti04}, where there is 
little relationship between stellar mass and the metallicity for massive 
systems, but at intermediate and lower masses the correlation is strong between 
the two quantities.

% ISM - inflows and outflows
The inflow and outflow of gas in galaxies are aspects of galaxy evolution that 
are not yet well understood.  This is especially important when studying dwarf 
galaxies, since their gravitational potential wells are potentially small enough 
to be strongly influenced by star formation and/or supernovae.  Simulations by 
\cite{Marcolini04} find that when ram pressure from the intergalactic medium 
(IGM) is comparable to the thermal pressure of the central interstellar medium 
(ISM), stripping and superwind influence each other and increase the gas removal 
rate.  They find that the amount of metal-rich ejecta is sensitive to the ram 
pressure.  
% supernova
Simulations by \cite{Power14} and \cite{Melioli15} show that supernovae contain 
sufficient energy to unbind the gas in a low mass halo.  \cite{Hu16} show that 
supernova-driven galactic outflows push metal-rich gas into the halo.  A small 
fraction of the gas eventually escapes the halo, while most falls back onto the 
disc.  This results in the halo metallicity being about 20\% higher than the 
disc metallicity.  Likewise, \cite{Muratov17} find that almost all metals 
produced in a Type II supernova are ejected from the galaxy.
% star formation
Unlike the supernovae, \cite{Melioli15} finds that the ISM material does not 
have a strong likelihood of being expelled from a galaxy due to star formation.  
In contrast, \cite{Muratov15} finds that a large portion of material is ejected 
in galactic outflows after a bust of star formation, which collects in the 
circumgalactic medium (CGM) and is sometimes recycled in later star formation 
episodes.  In galaxies with $M_h < 10^{12} M_\odot$, a fraction of material is 
lost to the IGM.

% Metallicity
In numerical simulations to study the properties of the ISM in an isolated, 
star-forming galaxy, \cite{Hu16} finds that stellar feedback slowly increases 
the disc metallicity.  The majority of outflows are enriched winds, which 
reduces the metallicity of the ISM.  \cite{Muratov17} finds that outflows to the 
CGM generated in dwarf galaxies at low redshifts are dominated by metal-poor 
gas.  Galaxies retain most of the metals they produce, though a large fraction 
is in the CGM.  By combining our observations with the results of these 
simulations, we can begin to understand how star formation and supernovae 
influence a dwarf galaxy's gas content.

>>>>

% Hierarchical formation of halos
It is impossible to directly observe the formation of a galaxy.  Based on 
detected merging galaxies, the astronomical community has surmised that galaxies 
have increased their mass largely due to the merging of smaller galaxies.  
$\Lambda$CDM simulations of hierarchical galaxy formation by \cite{deRossi07} 
find that the growth of systems by aggregation is responsible for the 
mass-metallicity relation.  Less massive systems tend to increase their stellar 
mass by either gas-rich mergers or secular evolution, resulting in a stronger 
correlation between stellar mass and metallicity.  Evidence of this is seen in 
the mass-metallicity relation of \cite{Tremonti04}, where there is little 
relationship between stellar mass and the metallicity for massive systems, but 
at intermediate and lower masses the correlation is strong between the two 
quantities.

% ISM - inflows and outflows
The inflow and outflow of gas in galaxies are aspects of galaxy evolution that 
are not yet well understood.  This is especially important when studying dwarf 
galaxies, since their gravitational potential wells may be shallow enough to be 
strongly influenced by star formation and/or supernovae.  Simulations by 
\cite{Marcolini04} find that when ram pressure from the intergalactic medium 
(IGM) is comparable to the thermal pressure of the central interstellar medium 
(ISM), stripping and superwind influence each other and increase the gas removal 
rate.  They find that the amount of metal-rich ejecta is sensitive to the ram 
pressure.  
% supernova
Simulations by \cite{Power14} and \cite{Melioli15} show that supernovae contain 
sufficient energy to unbind the gas in a low mass halo.  \cite{Hu16} show that 
supernova-driven galactic outflows push metal-rich gas into the halo.  A small 
fraction of the gas eventually escapes the halo, while most falls back onto the 
disc.  This results in the halo metallicity being about 20\% higher than the 
disc metallicity.  Likewise, \cite{Muratov17} find that almost all metals 
produced in a Type II supernova are ejected from the galaxy.
% star formation
Unlike the supernovae, \cite{Melioli15} finds that the ISM material does not 
have a strong likelihood of being expelled from a galaxy due to star formation.  
In contrast, \cite{Muratov15} finds that a large portion of material is ejected 
in galactic outflows after a bust of star formation, which collects in the 
circumgalactic medium (CGM) and is sometimes recycled in later star formation 
episodes.  In galaxies with $M_h < 10^{12} M_\odot$, a fraction of material is 
lost to the IGM.

% Metallicity
Numerical simulations that study the properties of the ISM in an isolated, 
star-forming galaxy find that stellar feedback slowly increases the disc 
metallicity \citep{Hu16}.  The majority of outflows are enriched winds, which 
reduces the metallicity of the ISM.  In dwarf galaxies at low redshifts, these 
outflows to the CGM are dominated by metal-poor gas \citep{Muratov17}.  While 
galaxies retain most of the metals they produce, a large fraction is in the CGM.  
By combining our observations with the results of these simulations, we can 
begin to understand how star formation and supernovae influence a dwarf galaxy's 
gas content.
